---
title: "DataSet Creation"
output: html_notebook
---

# Environment

```{r}
library(bigrquery)
library(summarytools)
library(dplyr)
library(plotly)
library(readxl)

asciify <- function(df, pad = 1, ...) {
    ## error checking
    stopifnot(is.data.frame(df))
    ## internal functions
    SepLine <- function(n, pad = 1) {
        tmp <- lapply(n, function(x, pad) paste(rep("-", x + (2* pad)),
                                                collapse = ""),
                      pad = pad)
        paste0("+", paste(tmp, collapse = "+"), "+")
    }
    Row <- function(x, n, pad = 1) {
        foo <- function(i, x, n) {
            fmt <- paste0("%", n[i], "s")
            sprintf(fmt, as.character(x[i]))
        }
        rowc <- sapply(seq_along(x), foo, x = x, n = n)
        paste0("|", paste(paste0(rep(" ", pad), rowc, rep(" ", pad)),
                          collapse = "|"),
               "|")
    }
    ## convert everything to characters
    df <- as.matrix(df)
    ## nchar in data
    mdf <- apply(df, 2, function(x) max(nchar(x)))
    ## nchar in names
    cnames <- nchar(colnames(df))
    ## max nchar of name+data per elements
    M <- pmax(mdf, cnames)
    ## write the header
    sep <- SepLine(M, pad = pad)
    writeLines(sep)
    writeLines(Row(colnames(df), M, pad = pad))
    writeLines(sep)
    ## write the rows
    for(i in seq_len(nrow(df))) {
        ## write a row
        writeLines(Row(df[i,], M, pad = pad))
        ## write separator
        writeLines(sep)
    }
    invisible(df)
}

```


## BigQuery related functions Set up

This chunks also creates the run_query and get_sql function.

```{r setup, include=FALSE}

project_id <- "hst-953-2018"
options(httr_oauth_cache=FALSE)
run_query <- function(query){
  data <- query_exec(query, project=project_id, use_legacy_sql=FALSE,max_pages = Inf)
  return(data)
}

# function for reading sql files
getSQL <- function(filepath){
  con = file(filepath, "r")
  sql.string <- ""

  while (TRUE){
    line <- readLines(con, n = 1)

    if ( length(line) == 0 ){
      break
    }

    line <- gsub("\\t", " ", line)

    if(grepl("--",line) == TRUE){
      line <- paste(sub("--","/*",line),"*/")
    }

    sql.string <- paste(sql.string, line)
  }

  close(con)
  return(sql.string)
}
```

# Creating the datasets

```{r}

demographics<-run_query(getSQL('sql/demographics.sql'))

gcs_baseline<-run_query(getSQL("sql/gcs_baseline.sql" ))

apache_groups<-run_query(getSQL('sql/apache_groups.sql')) 

apachescore<-run_query(getSQL('sql/apachescore.sql')) 

uniquepatients_first_icustay<-run_query(getSQL("sql/uniquepatients_first_icustay.sql" ))

code_status_adm_change<-run_query(getSQL("sql/code_status_adm_change.sql" ))

```



# Merge all datasets

We are using a left join to join them

```{r}
# left join = all.x=TRUE
adm_disorientation_risk_code_stat<-Reduce(function(...) merge(..., all.x=TRUE,by = "patientunitstayid"), list(
  uniquepatients_first_icustay
,demographics
,apache_groups
,apachescore
,code_status_adm_change	              
,gcs_baseline
))

adm_disorientation_risk_code_stat['gcs_after_discharge']<-if_else(
  critical_illness_confusion_df$gcs_abnormality_offset > critical_illness_confusion_df$iculos,1,0)
```

# We are creating a new variable.

If gcs abnormal is happening before discharge, we choose gcs abnormal offset, if discharge is happening before gcs abnormal, we choose discharge offset.

```{r}
adm_disorientation_risk_code_stat<-critical_illness_confusion_df%>%
  mutate(offset_of_analysis = case_when( gcs_abnormality_offset <= iculos ~ gcs_abnormality_offset
                                        ,gcs_abnormality_offset > iculos ~ iculos)
  )
```


# Dataset report

```{r}
dfSummary.html<-view(dfSummary(
adm_disorientation_risk_code_stat
))

system("wkhtmltopdf --javascript-delay 1 dfSummary.html dfSummary.pdf")
```

# Final variables wrangling

Some variables were mapped using JMP statistical software following the rules below:

*De-escalation of code status*
Was defined by an order to change code status to one of the following : Do nNot resuscitateResusciatate (n=5983), No Cardioversion(n=225), No Cardiopulmonary Resuscitation N=576), No Cardioversion (n=225), No Intubation(n=468), No Vasopressors/inotropes (n=60), Comfort Measures Only (n=104), ….” "code_descalation"   = recoded “adm_code_status_change”

Level   
Advance directives 
Comfort measures only 
Do not resuscitate 
No augmentation of care 
No blood draws 
No blood products 
No cardioversion 
No CPR 
No intubation 
No vasopressors/inotropes 
Total 

*time_to_event*

“Time to event was from ICU admission until code status change or censoring”. This means that I used either time to code descalation or length of ICU stay as time to event. Here is the code for that variable.

`If( :code descalation == 0, :Name( "ico los/hours" ), :adm_code_status_change_hrs)`

*disorientation*  

We defined disorientation as “confused”, having “inappropriate words” or “incomprehensible sounds”, but with a normal assessment of the GCS motor “obey commands” and eye opening “spontaneously” responses.
Here is the code for that variable:

`If(:gcs_motor_baseline == 6 & :gcs_eyes_baseline == 4 & 1 < :gcs_verbal_baseline <5,1,0)`









