---
title: "Survival Analysis"
output:
  html_notebook:
    toc: yes
---

# Enviroment 

```{r}
library(survival)
library(dplyr)
library(Deducer)
library(readxl)
library(ggplot2)
library(survminer)
library(jtools)
library(simPH)
```


# Loading our dataset

```{r}
#main_df <- 
```

# Main dataset

## Cox proportional hazards model 

##### Fitting survival data

```{r}
# Fit a Cox proportional hazards model
fit.coxph <- coxph(
  Surv(time_to_event, code_descalation==1) ~ 
          patientage 
          + patientgender
          + ethnicity 
          + unittype 
          + apachedxgroup 
          + apachescore 
          + disorientation 
          ,data = main_df)
```

### Hazard ratio per confounder

```{r fig.height=10, fig.width=10}
#ggforest(fit.coxph, data = main_df)
hr<-summary(fit.coxph)
hr_confint<-as.data.frame(hr$conf.int)
hr_confint<-hr_confint[,c(1,3,4)]
round(hr_confint,2)
```


# Apache quartiles

### Cox proportional hazard model per 

#### Quartile 1

##### Fitting survival data

```{r}
coxph_apache_q1 <-coxph( 
                   Surv(time_to_event, code_descalation==1) 
                     ~ patientage 
                     + patientgender 
                     + ethnicity 
                     + unittype 
                     + apachedxgroup 
                     + apachescore
                     + disorientation 
                     , data=subset(main_df,apache_quartiles==1)
                     )
```


##### Hazard ratio per confounder

```{r fig.height=10, fig.width=10}
#ggforest(coxph_apache_q1, data = main_df)
hr<-summary(coxph_apache_q1)
hr_confint<-as.data.frame(hr$conf.int)
hr_confint<-hr_confint[,c(1,3,4)]
round(hr_confint,2)
```

####  Quartile 2

##### Fitting survival data

```{r}
coxph_apache_q2 <-coxph( 
                   Surv(time_to_event, code_descalation==1) 
                     ~ patientage 
                     + patientgender 
                     + ethnicity 
                     + unittype 
                     + apachedxgroup 
                     + apachescore
                     + disorientation 
                     , data=subset(main_df,apache_quartiles==2)
                     )
```


##### Hazard ratio per confounder

```{r fig.height=10, fig.width=10}
#ggforest(coxph_apache_q2, data = main_df)
hr<-summary(coxph_apache_q2)
hr_confint<-as.data.frame(hr$conf.int)
hr_confint<-hr_confint[,c(1,3,4)]
round(hr_confint,2)
```

####  Quartile 3

##### Fitting survival data

```{r}
coxph_apache_q3 <-coxph( 
                   Surv(time_to_event, code_descalation==1) 
                     ~ patientage 
                     + patientgender 
                     + ethnicity 
                     + unittype 
                     + apachedxgroup 
                     + apachescore
                     + disorientation 
                     , data=subset(main_df,apache_quartiles==3)
                     )
```


##### Hazard ratio per confounder

```{r fig.height=10, fig.width=10}
#ggforest(coxph_apache_q3, data = main_df)
hr<-summary(coxph_apache_q3)
hr_confint<-as.data.frame(hr$conf.int)
hr_confint<-hr_confint[,c(1,3,4)]
round(hr_confint,2)
```

####  Quartile 4

##### Fitting survival data

```{r}
coxph_apache_q4 <-coxph( 
                   Surv(time_to_event, code_descalation==1) 
                     ~ patientage 
                     + patientgender 
                     + ethnicity 
                     + unittype 
                     + apachedxgroup 
                     + apachescore
                     + disorientation 
                     , data=subset(main_df,apache_quartiles==4)
                     )
```


##### Hazard ratio per confounder

```{r fig.height=10, fig.width=10}
#ggforest(coxph_apache_q4, data = main_df)
hr<-summary(coxph_apache_q4)
hr_confint<-as.data.frame(hr$conf.int)
hr_confint<-hr_confint[,c(1,3,4)]
round(hr_confint,2)
```


